Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-18 doc/manuscript/ESSDmanuscript.Rmd
added code to pull in some statistics

#Statistics
n_records_ForC= NA # total n records in ForC
n_plots_ForC = NA # total n plots in ForC
n_areas_ForC = NA # total n geographic areas in ForC
n_independent_records_ForC= NA #suspected duplicates removed
n_records_EFDB_variables= NA #n independent records relevant to EFDB
n_records_sent_to_EFDB = NA # n records sent to EFDB
n_records_posted_EFDB = NA # n records accepted and posted in EFDB

n_new_variables = 11 + 2 + 2 #delta. + woody.mortality + O horizon
# get n fields modified
sampling_details <- read.csv(paste0(path_to_ForC,"/ForC/database_management_records/record_of_changes.csv"), stringsAsFactors = FALSE, check.names = FALSE)
n_fields_modified =  length(sampling_details[,"Column"]) + 4 
n_records_checked = NA # this will be hard to get at, but we can at least estimate a minimum (= previously existing records in records sent to EFDB)
n_records_added = NA

>>>>

#Statistics
ForC_measurements <- read.csv(paste0(path_to_ForC,"/ForC/data/ForC_measurements.csv"), stringsAsFactors = FALSE, check.names = FALSE)
n_records_ForC= length(ForC_measurements[,"measurement.ID"])  # total n records in ForC

ForC_plots <- read.csv(paste0(path_to_ForC,"/ForC/data/ForC_plots.csv"), stringsAsFactors = FALSE, check.names = FALSE)
n_plots_ForC = length(ForC_plots[,"plot.ID"]) # total n plots in ForC

ForC_sites <- read.csv(paste0(path_to_ForC,"/ForC/data/ForC_sites.csv"), stringsAsFactors = FALSE, check.names = FALSE)
n_areas_ForC = max(ForC_sites$geographic.area, na.rm = TRUE) # total n geographic areas in ForC

n_independent_records_ForC= NA #suspected duplicates removed. This is the number of records fin ForC simplified.
n_records_EFDB_variables= NA #n independent records relevant to EFDB
n_records_sent_to_EFDB = NA # n records sent to EFDB
n_records_posted_EFDB = NA # n records accepted and posted in EFDB

n_new_variables = 11 + 2 + 2 #delta. + woody.mortality + O horizon
# get n fields modified
sampling_details <- read.csv(paste0(path_to_ForC,"/ForC/database_management_records/record_of_changes.csv"), stringsAsFactors = FALSE, check.names = FALSE)
n_fields_modified =  length(sampling_details[,"Column"]) + 4 
n_records_checked = NA # this will be hard to get at, but we can at least estimate a minimum (= previously existing records in records sent to EFDB)
n_records_added = max(ForC_measurements$measurement.ID) -48956 # Madison's entries start with measurement.ID = 48956

### 2022-04-18 doc/manuscript/ESSDmanuscript.tex
added code to pull in some statistics

The Global Forest Carbon Database, ForC
(\url{https://forc-db.github.io/}), is the largest collection of
published estimates of forest carbon stocks, increments, and annual
fluxes
\citep{anderson-teixeira_forc_2018, anderson-teixeira_carbon_2021}. For
C currently contains NA records from NA plots in NA distinct
geographical areas, along with records of stand age and disturbance
history. As such, ForC is positioned to improve forest C accounting
through the transfer of data to EFDB. The purpose of this publication is
to document that process and provide recommendations for future
improvements.

@@

In addition to reviewing existing records, we added a total of NA new
records to ForC. These included \textbf{\#\#} records from \textbf{\#\#}
studies \citep{piponiot_distribution_2022, refs} that were not
previously included in ForC. In addition, we created new records for
\textbf{\#\#} EFDB-relevant estimates presented in the original
publication that were not yet present in ForC.

@@

As of April 18, 2022, ForC (v4.0) contained NA independent records (NA
total), NA of which were for variables relevant to EFDB (Fig. 1). These
records were distributed across all forested continents and ecozones,
with particularly high concentrations in \emph{{[}ecozone(s){]}} and low
concentrations in \emph{{[}ecozone(s){]}} (Fig. 2). The most widely
represented forest type was \emph{{[}type{]}}, followed by
\emph{{[}type{]}} and \emph{{[}type{]}} (Fig. 3).

>>>>

The Global Forest Carbon Database, ForC
(\url{https://forc-db.github.io/}), is the largest collection of
published estimates of forest carbon stocks, increments, and annual
fluxes
\citep{anderson-teixeira_forc_2018, anderson-teixeira_carbon_2021}. For
C currently contains 39838 records from 10585 plots in 1531 distinct
geographical areas, along with records of stand age and disturbance
history. As such, ForC is positioned to improve forest C accounting
through the transfer of data to EFDB. The purpose of this publication is
to document that process and provide recommendations for future
improvements.

@@

In addition to reviewing existing records, we added a total of 305 new
records to ForC. These included \textbf{\#\#} records from \textbf{\#\#}
studies \citep{piponiot_distribution_2022, refs} that were not
previously included in ForC. In addition, we created new records for
\textbf{\#\#} EFDB-relevant estimates presented in the original
publication that were not yet present in ForC.

@@

As of April 18, 2022, ForC (v4.0) contained NA independent records
(39838 total), NA of which were for variables relevant to EFDB (Fig. 1).
These records were distributed across all forested continents and
ecozones, with particularly high concentrations in
\emph{{[}ecozone(s){]}} and low concentrations in
\emph{{[}ecozone(s){]}} (Fig. 2). The most widely represented forest
type was \emph{{[}type{]}}, followed by \emph{{[}type{]}} and
\emph{{[}type{]}} (Fig. 3).
